### 2016-05-08 document/manuscript-plos.tex
Update manuscript-plos.tex
I have modified the Affiliations section as requested by PLOS: all affiliations listed contain a Department, Institution, City, and Country (removing information such as street name and post/zip code).

\bf{1} European Molecular Biology Laboratory, European Bioinformatics
Institute (EMBL-EBI), Wellcome Trust Genome Campus, Hinxton,
Cambridge, CB10 1SD, UK.
\\
\bf{2} Computational Proteomics Unit, Cambridge Systems Biology
Centre, University of Cambridge, Tennis Court Road, Cambridge, CB2
1GA, UK.
\\
\bf{3} Applied Bioinformatics and Department of Computer Science,
University of Tübingen, D-72074 Tübingen, Germany.
\\
\bf{4} Medizinisches Proteom-Center, Ruhr-Universität Bochum,
Universitätsstr. 150, D-44801 Bochum, Germany.
\\
\bf{5} Department of Pathology, University of Michigan, Ann Arbor,
Michigan 48109, USA.
\\
\bf{6} Institute of Plant Biology and Biotechnology, University of
Muenster, Schlossplatz 8, 48143 Muenster, Germany.
\\
\bf{7} Centre for Mathematical Sciences, University of Cambridge,
Wilberforce Road, Cambridge CB3 0WA, UK.
\\
\bf{8} National Center for Supercomputing Applications \& Graduate
School of Library and Information Science, University of Illinois,
1205 W. Clark St., Urbana, Illinois 61801, USA.
\\
\bf{9} MIT Laboratory for Computational Physiology, Institute for
Medical Engineering and Science, Massachusetts Institute of
Technology, Cambridge, MA 02142, USA.
\\
\bf{10} Centre for Interdisciplinary Research in Computational
Algebra, University of St Andrews, St Andrews, Fife, KY16 9SX, UK.
\\
\bf{11} Department of Molecular Biology and Biochemistry, Markey
Cancer Center, Resource Center for Stable Isotope-Resolved
Metabolomics, University of Kentucky, 800 Rose Street Lexington, KY
40536-0093, USA.
\\
\bf{12} The Novo Nordisk Foundation Center for Biosustainability,
Technical University of Denmark, Kogle Alle 6, 2970 Hørsholm, Denmark

@@

>>>>

\bf{1} European Molecular Biology Laboratory, European Bioinformatics
Institute (EMBL-EBI), Wellcome Trust Genome Campus, Hinxton,
Cambridge, UK.
\\
\bf{2} Computational Proteomics Unit, Cambridge Systems Biology
Centre, University of Cambridge, Cambridge, UK.
\\
\bf{3} Applied Bioinformatics and Department of Computer Science,
University of Tübingen, Tübingen, Germany.
\\
\bf{4} Medizinisches Proteom-Center, Ruhr-Universität Bochum, Bochum, Germany.
\\
\bf{5} Department of Pathology, University of Michigan, Ann Arbor,
Michigan, USA.
\\
\bf{6} Institute of Plant Biology and Biotechnology, University of
Muenster, Muenster, Germany.
\\
\bf{7} Centre for Mathematical Sciences, University of Cambridge,
Cambridge, UK.
\\
\bf{8} National Center for Supercomputing Applications \& Graduate
School of Library and Information Science, University of Illinois,
Urbana, Illinois, USA.
\\
\bf{9} MIT Laboratory for Computational Physiology, Institute for
Medical Engineering and Science, Massachusetts Institute of
Technology, Cambridge, MA, USA.
\\
\bf{10} Centre for Interdisciplinary Research in Computational
Algebra, University of St Andrews, St Andrews, UK.
\\
\bf{11} Department of Molecular Biology and Biochemistry, Markey
Cancer Center, Resource Center for Stable Isotope-Resolved
Metabolomics, University of Kentucky, Lexington, KY, USA.
\\
\bf{12} The Novo Nordisk Foundation Center for Biosustainability,
Technical University of Denmark, Hørsholm, Denmark.

@@

\section*{Supporting Information Legends}

\textbf{Supplementary File S1.} Supplementary Information including
three sections: Git Large File Storage (LFS), Testing Levels of the
Source Code and Continuous integration, and Source code documentation.
